Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-08 thesis/acknowledgments.tex
adding software

>>>>

Finally, I would like to thank the numerous developers and contributors to the
open-source software packages without which this \dissertation would not be
possible. This includes more general software, such as \textsc{Python}, \textsc{IPython}, \textsc{NumPy},
\textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py},
and \textsc{deepdish}, and more astronomy-specific projects like  \textsc{yt}, \textsc{Enzo},
\textsc{Grackle}, \textsc{AstroPy}, and \textsc{Cloudy}. In particular I would like
to thank the many developers of \textsc{yt}, \textsc{Enzo}, and \textsc{Grackle}
who have helped answer questions, debug code, and implement new features on
my behalf throughout this process. This includes: Britton Smith, Nathan Goldbaum,
John Wise, Matt Turk, Greg Bryan, Simon Glover, Munier Salem, Cameron Hummels,
Christine Simpson, and Brian O'Shea.
